Data simulations

### 2019-08-28 analysis/data_simulations.Rmd
add second simulation

>>>>

```{r}
library(bindata)

# Parameters of joint distribution
size <- 1
p1 <- 0.7
p2 <- 0.6
rho<- 0.3

# Create one pair of correlated binomial values
trials <- rmvbin(size, c(p1,p2), bincorr=(1-rho)*diag(2)+rho)
colSums(trials)

# A function to create n correlated pairs
rmvBinomial <- function(id, n, size, p1, p2, rho) {
    X <- replicate(n, {
             colSums(rmvbin(size, c(p1,p2), bincorr=(1-rho)*diag(2)+rho))
         })
    t(X)%>%
  as_tibble()%>%
      mutate(trial = 1:n, 
             id = id)%>%
      gather(task, score, -trial, -id)
}
# Try it out, creating 1000 pairs

sim2 <- function (seed, n_trials) {

n_sub = 100

tibble(id = 1:n_sub) %>% 
  mutate(tidy = map(id, rmvBinomial, n =n_trials, size=size, p1=p1, p2=p2, rho=rho))%>%
  unnest(tidy)%>%
  group_by(id, task)%>%
  summarise(mean= mean(score))%>%
  spread(task, mean)%>%
  ungroup()%>%
  summarise(cor = cor(V1,V2))

}

cor_sim_5 <- tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim2, n_trials = 5))%>%
  unnest(tidy)%>%
  mutate(trials = "5")

cor_sim_4 <- tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim2, n_trials = 4))%>%
  unnest(tidy)%>%
  mutate(trials = "4")

cor_sim_3 <- tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim2, n_trials = 3))%>%
  unnest(tidy)%>%
  mutate(trials = "3")

cor_sim_2 <- tibble(seed = 1:n_sim) %>% 
  mutate(tidy = map(seed, sim2, n_trials = 2))%>%
  unnest(tidy)%>%
  mutate(trials = "2")

sim_plot_cor = bind_rows(
  cor_sim_5,
  cor_sim_4,
  cor_sim_3,
  cor_sim_2
)

ggplot(sim_plot_cor, aes(x = cor, fill = trials))+
  geom_density(alpha = .5)+
  geom_vline(xintercept = .3)+
  xlim(0,1)+
  theme_few()+
  scale_fill_ptol()
```
